Modal Verification Patterns for Systems

### 2025-06-25 paper.tex
fix option clash
some tweak

\usepackage{booktabs}
\usepackage{multirow}
 \usepackage{proof}
\usepackage{array}
\newcolumntype{O}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{Q}[1]{>{\raggedleft\arraybackslash}m{#1}}
\newcolumntype{S}{>{\centering\arraybackslash}m{2cm}}

\usepackage{microtype}%if unwanted, comment out or use option "draft"
%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
%\usepackage{t1enc}
%\usepackage[strings]{underscore}
%%%%%\usepackage{geometry}
\usepackage{wrapfig}
\usepackage[rawfloats=true]{floatrow} 
\restylefloat{figure}    
\DeclareMathSizes{4}{4}{4}{4}
\usepackage{varwidth}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage[fleqn]{amsmath}
\usepackage{mathtools}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xspace}
\usepackage{listings}
\usepackage{comment}
\usepackage{longtable}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage[toc,page]{appendix}
\usepackage[export]{adjustbox}
\usepackage{amssymb}
\usepackage{graphics,graphicx}
\usepackage{mathpartir}
\usepackage{array}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc, shapes, backgrounds}
\usepackage{verbatim}
\usepackage{tikz-qtree}
\usepackage{pgfplots}
\usepackage{caption,capt-of}
\usepackage{color}
\usepackage{soul}
\setul{1ex}{0.8ex}
\definecolor{orange}{rgb}{1,0.5,0}
\setulcolor{orange}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{afterpage}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage{rotating}

@@

\paragraph{Weak-Memory} When considering weak memory models, we also want points-to information (address-value mappings).

@@

This choice trades off complexity against flexibility and scoping constraints.
Strongly nominalized elements track additional specifier/prover-visible book-keeping data.
But in exchange for carrying those identifiers of their context with them, 
strongly nominalized elements can be used together under any modality. For example, one can
use the StackRegion modality to talk about two different stack frames simultaneously for code
which accesses multiple stack frames: $\fbox{n} \; \ell \mapsto v \ast \fbox{n+1} \; \ell' \mapsto v'$.
Using a given strongly nominalized assertion element under different modalities for different
frames does not change its meaning.

>>>>

\usepackage{booktabs}
\usepackage{multirow}
 \usepackage{proof}
 \usepackage{array}
 \usepackage{iris}
\newcolumntype{O}[1]{>{\raggedright\arraybackslash}m{#1}}
\newcolumntype{P}[1]{>{\centering\arraybackslash}m{#1}}
\newcolumntype{Q}[1]{>{\raggedleft\arraybackslash}m{#1}}
\newcolumntype{S}{>{\centering\arraybackslash}m{2cm}}

\usepackage{microtype}%if unwanted, comment out or use option "draft"
%\graphicspath{{./graphics/}}%helpful if your graphic files are in another directory
%\usepackage{t1enc}
%\usepackage[strings]{underscore}
%%%%%\usepackage{geometry}
\usepackage{wrapfig}
\usepackage[rawfloats=true]{floatrow} 
\restylefloat{figure}    
\DeclareMathSizes{4}{4}{4}{4}
\usepackage{varwidth}
\usepackage{lmodern}
\usepackage{amsfonts}
\usepackage[fleqn]{amsmath}
\usepackage[fleqn]{mathtools}
\usepackage{amssymb}
\usepackage{hyperref}
\usepackage{proof}
\usepackage{stmaryrd}
\usepackage{xspace}
\usepackage{listings}
\usepackage{comment}
\usepackage{longtable}
\usepackage{float}
\usepackage[section]{placeins}
\usepackage[toc,page]{appendix}
\usepackage[export]{adjustbox}
\usepackage{amssymb}
\usepackage{graphics,graphicx}
\usepackage{mathpartir}
\usepackage{array}
\usepackage{tikz}
\usetikzlibrary{shapes.geometric}
\usetikzlibrary{arrows.meta,arrows}
\usetikzlibrary{positioning}
\usetikzlibrary{calc, shapes, backgrounds}
\usepackage{verbatim}
\usepackage{tikz-qtree}
\usepackage{pgfplots}
\usepackage{caption,capt-of}
\usepackage{color}
\usepackage{soul}
\setul{1ex}{0.8ex}
\definecolor{orange}{rgb}{1,0.5,0}
\setulcolor{orange}
\usepackage{subcaption}
\usepackage{lipsum}
\usepackage{afterpage}
\usepackage{fontawesome}
\usepackage[utf8]{inputenc}
\usepackage{rotating}

@@

\paragraph{Weak-Memory} When considering weak memory models, we consider address-value mappings of thread-local views in C11 memory model~\cite{lahav2017repairing}). Modalities $\Delta_\pi(P)$ and $\nabla_\pi(P)$ with $P$ represent the memory address-value mappings that held before or will hold after certain memory fence operations by thread $\pi$.

@@

This choice trades off complexity against flexibility and scoping constraints.
Strongly nominalized elements track additional specifier/prover-visible book-keeping data.
But in exchange for carrying those identifiers of their context with them, 
strongly nominalized elements can be used together under any modality. For example, one can
use the StackRegion modality to talk about two different stack frames simultaneously for code
which accesses multiple stack frames: $\fbox{n} \; \ell \mapsto v \ast \fbox{n+1} \; \ell' \mapsto v'$.
Using a given strongly nominalized assertion element under different modalities for different
frames does not change its meaning. Likewise,  weak-memory specific modalities existentially quantify over other views, related to the ``current'' view (the one where
the current thread's assertions are evaluated), and evaluate a resource (an thread-local view of an address-value mapping) with respect to those other views. Although it looks like the pattern we see in the VMM case,
It is \emph{not}, however, an instance of hybrid logic, which is specifically demarcated by an assertion language where
\emph{assertions}, not their semantics, choose and name the evaluation points for modal assertions.
A hybrid extension of the aforementioned logics would include assertions which named specific views at which to evaluate
$P$, in the syntax of the assertion (e.g., $\Delta_\pi^v(P):=\lambda\_\ldotp (P\;v)$) rather than the 
$\Delta_\pi(P):= \lambda v\ldotp (\exists v_{rel}\ldotp \ownGhost{\pi}{\mathsf{RelV}(v_{rel})\;v} \ast (P\;v_{rel})))$ actually used.
Note the hybrid version takes the place to evaluate $P$ as a parameter, and therefore allows the \emph{derived} (modal) logic to explicitly
reason in terms of evaluation points, rather than hiding all points of evaluation in the internal definitions of modalities.
